Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-24 paper/ijcai/paper.tex
more updates

If we consider only the faults which can benefit from our approach, we can observe that there is a considerable
amount of cases where the approach is actually successful. For
$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
on the ranking and an impressive maximum ranking improvement
of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
achieves a mean improvement of $19$ ($13.35\%$ on average) statements
on the ranking and a maximum ranking improvement
of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.
In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. 
In bold, we present the results of the $227$ faults that do not contain the 
cases that are result of the limitations mentioned before (test design and fault of omission). Inside parentheses, we present the
rank results for all faults. The \combpar{k} combination yields an improvement
of $17.3$ on the rank mean of the dataset faulty statements when using $k=5$.
Instead, if $k=10$ is considered, the proposed approach returns an improvement of
$6.1$ on the rank mean of all faulty statements.
These $227$ faults contain cases where the faulty class was not in the choosen 
set of classes $k$ and a high amount of cases where the improvement was none.

@@

\Rui{Weakness: there has to be discussion on whether there is potential/promising
results somewhere.}

@@

\subsection{Threats to validity}

%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
It is importance to notice that our study does not evaluate the fault of the \closure{}
project since it requires high CPU to perform the \combpar{k} evaluation.

@@

\Fix{
The main lesson of this work is that
fault localization research should consider compare new techniques
against this combination.}

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (DS)
and Spectrum-based Fault Localization (SFL) are very popular fault diagnosis t
echniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining DS with SFL. The results of our empirical study show that, in
practice, DS rarely misses faulty statements (23 misses in 260 cases) and that
the DS-SFL combination improves the diagnostic accuracy in 51\% of the faults.
Hence, we found that, despite tacit opinions of the research community about
the usefulness of DS in automated debugging, we found the combination practical
and effective, and encourage new SFL techniques to be evaluated against that
optimization.

Future work is as follows: bla bla.

>>>>

In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$. 
In bold, we present the results of the $227$ faults that do not comprise the 
cases that are result of the limitations mentioned before (test design and fault of omission). These results show that \ds{} improves \sfl{} in a mean
of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements, when considering $k=10$. Inside parentheses, we present the
rank results for all faults which do not report promissing results. However, If we only consider the faults which can benefit from our approach, we can observe that there is a considerable
amount of cases where the approach is actually successful. For
$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ on average) statements
on the ranking and an impressive maximum ranking improvement
of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
achieves a mean improvement of $19$ ($13.35\%$ on average) statements
on the ranking and a maximum ranking improvement
of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.

@@

@@

\subsection{Threats to validity}
%
A potential threat to external validity related to the set of programs used in
our study. When choosing the projects for our study, our aim was to opt for
projects that resemble a general and large-sized application. To reduce
selection bias and facilitate the comparison of our results, we decided to
choose a benchmark that is popular in the community~\cite{just-defects4j-issta2014}.
It is importance to notice that our study does not evaluate the fault of the \closure{}
project since it requires high CPU to perform the \combpar{k} evaluation.

@@

Several approaches have been proposed in the literature to improve debugging
costs through automated software fault diagnosis to reduce time-to-market,
while maintaining high quality standards. In this domain, Dynamic Slicing (\ds)
and Spectrum-based Fault Localization (\sfl) are very popular fault diagnosis techniques and normally seen as complementary. This paper reports the outcome of
a study using real-world applications with the goal of demystifying the impact
of combining \ds~with \sfl. The results of our empirical study show that, in
practice, \ds~rarely misses faulty statements $9\%$ ($23$ misses in $260$ cases) and that
the \ds-\sfl~combination, coined as \combpar{k}, 
improves the diagnostic accuracy up to $73.7\%$ ($13.4\%$ on average).
Hence, we found that, despite tacit opinions of the research community about
the usefulness of \ds~in automated debugging, we found the combination practical
and effective, and encourage new \sfl~techniques to be evaluated against that
optimization.

Future work is as follows:
